\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars \vspace{-0.5cm}

### 2017-06-26 paper/ms.tex
Add separated lithium line figure

% metallicity and abundance difference
However, one of the stars, \bizarreone, is significantly more metal rich than
the other by 0.2~dex in \feh\ ($\approx 60\%$ in number density;
\figname~\ref{fig:abundances}).
Moreover, not all elements are equally enhanced: the abundances of \bizarreone\
show selective under-enhancement in \elem{C}, \elem{N}, \elem{O}, \elem{Na},
and \elem{Mn} relative to \elem{Fe} and other refractory elements.
As expected from their measured metallicity difference, the ratio of spectral
data and model between the two stars show significant residuals of almost all
metal line features, largely dominated by \elem{Fe}.
However, for absorption lines of elements that are not as enhanced in
\bizarreone\, the residuals are much smaller in amplitude demonstrating the
validity of the measured abundance differences (\figname~\ref{fig:spec1} and
\ref{fig:spec2}).

@@

% high Li
Both stars have high surface \elem{Li} abundances considering
their ages of $\sim 4$~Gyr.
The surface lithium abundance in a sun-like star decreases with its age due to
mixing induced by convection or rotation, which brings the lithium into the
interior ($T>2.5 \times 10^{6}$~K) where it is destroyed by proton capture
burning. %TODO: REFERENCE?
The \elem{Li} doublet at $6707.6$~\AA, which is usually too weak to be
detectable at this age even for high signal-to-noise spectra, is clearly
visible in the spectra of both stars (\figname~\ref{fig:spec2}).
The measured absolute abundances for \bizarreone\ and \sunanalog\ are
$2.75$~dex and $2.25$~dex, respectively (Myles \etal, in prep.),
resulting in the largest abundance difference ($\approx 0.5$~dex) seen
among all measured elements.

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{spec2.pdf}
  \caption{Same as \figname~\ref{fig:spec1}
    but for smaller portions of spectra at longer wavelengths that are
    not dominated by \elem{Fe}.
    We mark elements that give rise to strong absorption lines.
    The feature in the third column of the second row is a strong \elem{Li}
    line that was studied separately in Myles \etal\ (in prep.).
    Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
    in \bizarreone\ relative to \elem{Fe} or other refractory elements,
    show noticeably weaker residuals compared to neighboring lines of
    refractory elements.
  }
  \label{fig:spec2}
\end{figure}

>>>>

% metallicity and abundance difference
However, one of the stars, \bizarreone, is significantly more metal rich than
the other by 0.2~dex in \feh\ ($\approx 60\%$ in number density;
\figname~\ref{fig:abundances}).
Moreover, not all elements are equally enhanced: the abundances of \bizarreone\
show selective under-enhancement in \elem{C}, \elem{N}, \elem{O}, \elem{Na},
and \elem{Mn} relative to \elem{Fe} and other refractory elements.
As expected from their measured metallicity difference, the ratio of spectral
data and model between the two stars show significant residuals of almost all
metal line features, largely dominated by \elem{Fe}.
However, for absorption lines of elements that are not as enhanced in
\bizarreone\, the residuals are much smaller in amplitude demonstrating the
validity of the measured abundance differences (\figname~\ref{fig:spec1},
\ref{fig:spec2} and \ref{fig:spec_lithium}).

@@

% high Li
Both stars have high surface \elem{Li} abundances considering
their ages of $\sim 4$~Gyr.
The surface lithium abundance in a sun-like star decreases with its age due to
mixing induced by convection or rotation, which brings the lithium into the
interior ($T>2.5 \times 10^{6}$~K) where it is destroyed by proton capture
burning. %TODO: REFERENCE?
The \elem{Li} doublet at $6707.6$~\AA, which is usually too weak to be
detectable at this age even for high signal-to-noise spectra, is clearly
visible in the spectra of both stars (\figname~\ref{fig:spec_lithium}).
The measured absolute abundances for \bizarreone\ and \sunanalog\ are
$2.75$~dex and $2.25$~dex, respectively (Myles \etal, in prep.),
resulting in the largest abundance difference ($\approx 0.5$~dex) seen
among all measured elements.

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{spec2.pdf}
  \caption{Same as \figname~\ref{fig:spec1}
    but for smaller portions of spectra at longer wavelengths that are
    not dominated by \elem{Fe}.
    We mark elements that give rise to strong absorption lines.
    Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
    in \bizarreone\ relative to \elem{Fe} or other refractory elements,
    show noticeably weaker residuals compared to neighboring lines of
    refractory elements.
  }
  \label{fig:spec2}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.6\linewidth]{spec_lithium.pdf}
  \caption{Lithium lines in the spectra of \bizarreone\ and \sunanalog.
    This line is studied in Myles \etal\ (in prep.).
    Line legends are the same as in \figname~\ref{fig:spec1}.
  }
  \label{fig:spec_lithium}
\end{figure}
